\documentclass{article}
\begin{document}
\begin{center}\Huge{\bf Prateek Singhal}\end{center}
\rule{\textwidth}{1pt}
\large
\vspace{.1in}
\emph{Permanent Address}\\
35-C/4, Civil lines,\\
Janki Flats, \\
Bareilly - 243001.\vspace{.1in}\\
\emph{Present Address}\vspace{.1in}\\
The LNM Institute of Information Technology,\\
Rupa ki Nangal, Post-Sumel, Via-Jamdoli,\\
Jaipur-302031,\\
(Rajasthan) INDIA.\\
\begin{center}\Large{\bf \underline{Education}}\end{center}\vspace{.1in}
\begin{itemize}
\item \emph{High School}- G.P.M. Inter College, Bareilly.\\ 
         ICSE Board 2009.\\
         Percentage : 92.7 \%\\
\item \emph{Intermediate}- G.P.M. Inter College, Bareilly.\\
	ISC Board 2011.\\
	Percentage : 93.5 \%\\
\item \emph{Graduation}- The LNMIIT, Jaipur.\\
	Pursuing B.tech in Computer Science and Engineering.\\
\end{itemize}
\vspace{.1in}
\begin{center}\Large{\bf \underline{Computer Skills}}\end{center}\vspace{.1in}
\begin{itemize}
\item \emph{Languages}- JAVA,C,Python,SED,AWK,Perl,Shell scripting,\LaTeX,HTML,BASIC.
\item \emph{Operating systems}- Unix,Ubuntu,Fedora,Windows 98,Windows 2000,Windows XP,Windows 7.
\item \emph{Misc}- Office,Good Sufing skills, Good awareness of utility softwares.
\end{itemize}
\vspace{.1in}
\begin{center}\Large{\bf \underline{Community Service}}\end{center}\vspace{.1in}
\begin{itemize}
\item Discipline Incharge in Intermediate.
\item Volunteer in VOGUE- Fashion Parade at The LNMIIT.
\item Volunteer in IEEE conference by W3C India on HTML-5 at The LNMIIT.
\item Volunteer in The Litrary Committee during Vivacity-2012-Techno management cultural fest of The LNMIIT.
\end{itemize}
\vspace{.1in}
\begin{center}\Large{\bf \underline{Communication}}\end{center}\vspace{.1in}
\begin{itemize}
\item Done anchoring in the College Annual Function.
\item Part of the College Interaction team for The techno management cultural fest,Vivacity-2012.
\end{itemize}
\vspace{.1in}
\begin{center}\Large{\bf \underline{Special skills}}\end{center}\vspace{.1in}
\begin{itemize}
\item \emph{Writing}: Algorithms,Essays,Event reports,Formal and informal letters and e-mails.
\item \emph{Editing}: Photo editing in Adobe photoshop, Website design and editing templates.
\end{itemize}

\vspace{.1in}
\begin{center}\Large{\bf \underline{Honors and Achievements}}\end{center}\vspace{.1in}
\begin{itemize}
\item Two times District Topper of National Science Olympiad in class 9th and 10th.
\item School Topper in International Mathematics Olympiad in class 10th.
\item 6th Rank in the Intra University Programming Contest at The LNMIIT.
\item 2nd District Topper in High school.
\item 4th District Topper in Intermediate.
\end{itemize}
\vspace{.1in}
\begin{center}\Large{\bf \underline{Interests and Activities}}\end{center}\vspace{.1in}
\begin{itemize}
\item \emph{Sports}: Badminton,Cricket,Table Tennis,Chess,Carrom,Volley Ball.
\item Net surfing,Cyber Gaming, Computer programming,Website Designing.
\item Writing Poems,Listening Music,Stamp Collection.
\end{itemize}
\rule{\textwidth}{1pt}
\end{document}